Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study

### 2024-11-04 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd
x

# rating scales
df_sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201,
               223),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>% 
  rename(Participant = ID) %>%
  group_by(Participant) %>% 
  summarise(
    Mean_disrupption_appraisal = round(mean(disruption_appraisal), 2),
    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
    )%>% 
  dplyr::select(Participant,
                Mean_disrupption_appraisal,
                Mean_confidence_appraisal)

@@

# merge all data frames in list
df_merge <-
  df_list %>% reduce(full_join, by='Participant') %>%
  # filter(`Teaching Experience` > 0) %>% 
  dplyr::select(Stud_number_fixation_min,
                Average_duration_stud,
                Number_of_fixations.Disruptive_Person,
                Average_duration_disrup,
                Disrup_time_fixation_sec,
                GRI_mtu,
                SJT_All,
                SJT_Monitoring,
                Quest_All
                )

@@

# p-value for GRI x STJ_Monitoring
cor.test(df_merge$GRI_mtu, df_merge$SJT_Monitoring)

>>>>

# rating scales
df_sri <-
  excel_sheets("data/Coding_SRI.xlsx") %>%
  map_df(~ read_xlsx("data/Coding_SRI.xlsx", .)) %>%
  filter(
    !ID %in% c(201,
               223),
    !disruption_appraisal == -100,
    !confidence_appraisal == -100,
    !disruption_appraisal == -99,
    !confidence_appraisal == -99,
    !disruption_appraisal == -88,
    !confidence_appraisal == -88,
    !prevalence_rating == -100,
    !prevalence_rating == -99,
    !prevalence_rating == -88
    ) %>% 
  rename(Participant = ID) %>%
  group_by(Participant) %>% 
  summarise(
    Mean_disruption_appraisal = round(mean(disruption_appraisal), 2),
    Mean_confidence_appraisal = round(mean(confidence_appraisal), 2),
    Mean_prevalence_rating = round(mean(prevalence_rating), 2)
    )%>% 
  dplyr::select(Participant,
                Mean_disruption_appraisal,
                Mean_confidence_appraisal)

@@

# merge all data frames in list
df_merge <-
  df_list %>% reduce(full_join, by='Participant') %>%
  # filter(`Teaching Experience` > 0) %>% 
  dplyr::select(GRI_mtu,
                SJT_All,
                Quest_All,
                Mean_disruption_appraisal,
                Mean_confidence_appraisal
                )

@@

# p-value for GRI x Quest_All
cor.test(df_merge$GRI_mtu, df_merge$Quest_All)

# p-value for GRI x Disruption Rating
cor.test(df_merge$GRI_mtu, df_merge$Mean_disruption_appraisal)

# p-value for GRI x Confidence Rating
cor.test(df_merge$GRI_mtu, df_merge$Mean_confidence_appraisal)

### 2024-11-04 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.tex
x

\begin{verbatim}
## 
##  Pearson's product-moment correlation
## 
## data:  df_merge$GRI_mtu and df_merge$SJT_Monitoring
## t = -1.9731, df = 80, p-value = 0.05194
## alternative hypothesis: true correlation is not equal to 0
## 95 percent confidence interval:
##  -0.413114345  0.001665702
## sample estimates:
##        cor 
## -0.2154193
\end{verbatim}

>>>>

\begin{verbatim}
## 
##  Pearson's product-moment correlation
## 
## data:  df_merge$GRI_mtu and df_merge$Quest_All
## t = 0.64655, df = 80, p-value = 0.5198
## alternative hypothesis: true correlation is not equal to 0
## 95 percent confidence interval:
##  -0.1472121  0.2846518
## sample estimates:
##        cor 
## 0.07209825
\end{verbatim}

\begin{verbatim}
## 
##  Pearson's product-moment correlation
## 
## data:  df_merge$GRI_mtu and df_merge$Mean_disruption_appraisal
## t = 0.60918, df = 80, p-value = 0.5441
## alternative hypothesis: true correlation is not equal to 0
## 95 percent confidence interval:
##  -0.1512868  0.2808174
## sample estimates:
##        cor 
## 0.06795118
\end{verbatim}

\begin{verbatim}
## 
##  Pearson's product-moment correlation
## 
## data:  df_merge$GRI_mtu and df_merge$Mean_confidence_appraisal
## t = -0.11168, df = 80, p-value = 0.9114
## alternative hypothesis: true correlation is not equal to 0
## 95 percent confidence interval:
##  -0.2288719  0.2050778
## sample estimates:
##        cor 
## -0.0124849
\end{verbatim}
